{Supporting Information for 'Efficient Detection and Classification of Epigenomic Changes Under Multiple Conditions' by Pedro L. Baldoni$^*$, Naim U. Rashid$^*$, and Joseph G. Ibrahim$^*$}

### 2021-02-19 Latex/appendix/webappendix.Rnw
Updating tex

@@

@@

>>>>

\pagebreak
\clearpage

@@

\subsubsection{Simulation Study}

\begin{figure}[h]
\begin{center}
\centerline{\includegraphics[scale = 0.75]{../../Supp/Figure_Simulation_GC/Summary_Scatter_G113G233.png}}
\end{center}
\caption{Simulation study for GC-content bias correction with epigraHMM. In (A), example of a genomic region from the simulated data. In (B), simulated GC content effect on ChIP-seq counts. Scenario: low depth in condition 1, high depth in condition 2; positive GC effect on ChIP-seq counts in both conditions.
\label{fig:sim_gc_scatter}}
\end{figure}

\begin{figure}[h]
\begin{center}
\centerline{\includegraphics[scale = 0.75]{../../Supp/Figure_Simulation_GC/Summary_FDR_G113G233.png}}
\end{center}
\caption{Simulation study for GC-content bias correction with epigraHMM. Average observed true positive rate (y-axis) and observed false discovery rate (x-axis) in 100 simulated data sets for four different GC-content bias correction strategies: naive model without normalization for sequencing depth or GC-content bias, GC-content adjusted model, sequencing depth adjusted model, and GC-content and sequencing depth adjusted model. Optimal results are obtained only when the effect of GC-content is considered together with normalization for depth. The GC-content bias was accounted via model offsets in epigraHMM using the normalizing denominators from \cite{teng2017accounting}.
\label{fig:sim_gc_fdr}}
\end{figure}

\begin{figure}[h]
\begin{center}
\centerline{\includegraphics[scale = 0.75]{../../Supp/Figure_Simulation_GC/Summary_ROC_G113G233.png}}
\end{center}
\caption{Simulation study for GC-content bias correction with epigraHMM. Observed sensitivity (y-axis) and observed 1-specificity (x-axis) for each of the 100 simulated data sets four different GC-content bias correction strategies: naive model without normalization for sequencing depth or GC-content bias, GC-content adjusted model, sequencing depth adjusted model, and GC-content and sequencing depth adjusted model. Optimal results are obtained only when the effect of GC-content is considered together with normalization for depth. The GC-content bias was accounted via model offsets in epigraHMM using the normalizing denominators from \cite{teng2017accounting}. Dashed lines connect the observed metrics for each simulated dataset.
\label{fig:sim_gc_roc}}
\end{figure}

\pagebreak
\clearpage

@@

\begin{figure}[h]
\begin{center}
\centerline{\includegraphics[scale = 0.75]{../../Supp/Figure_BIC/H3K36me3_3G_4R_1e+05W_100SNR_bic.png}}
\end{center}
\caption{Simulation study for model selection via BIC. Simulation scenario: H3K36me3 data, 3 conditions, 4 replicates per condition, $10^5$ genomic windows, observed (estimated from ENCODE) SNR.
\label{fig:bic_4rep}}
\end{figure}

\begin{figure}[h]
\begin{center}
\centerline{\includegraphics[scale = 0.75]{../../Supp/Figure_BIC/H3K36me3_3G_2R_1e+05W_100SNR_bic.png}}
\end{center}
\caption{Simulation study for model selection via BIC. Simulation scenario: H3K36me3 data, 3 conditions, 2 replicates per condition, $10^5$ genomic windows, observed (estimated from ENCODE) SNR.
\label{fig:bic_2rep}}
\end{figure}

\begin{figure}[h]
\begin{center}
\centerline{\includegraphics[scale = 0.75]{../../Supp/Figure_BIC/H3K36me3_3G_1R_1e+05W_100SNR_bic.png}}
\end{center}
\caption{Simulation study for model selection via BIC. Simulation scenario: H3K36me3 data, 3 conditions, 1 replicate per condition, $10^5$ genomic windows, observed (estimated from ENCODE) SNR.
\label{fig:bic_1rep}}
\end{figure}

\pagebreak
\clearpage
